Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach

### 2017-03-08 sections0.08/results0.08.tex
change intro part on how using K -means and what is the different between K-means and SOM

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
    Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find \textbf{\textcolor{red}{the optimum.}}
    %We create the final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 1000, 0.9, 0.02, and 1, respectively.

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
    \textbf{We applied K-means clustering method (Section~\ref{sec: Kmeansvssom}) on both the template and sample galaxies and compared their results with the results of the 1D SOMs.}
    \textbf{\textcolor{red}{For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network is $12\times12$ and created two types of SOM to show different applications of 2D SOMs.}}

@@

            Figs.~\ref{fig: 1by2T} --\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
            The upper part of the figures shows the neurons and the relative distances \textbf{\textcolor{red}{between their weights}}. 
            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                  \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. The upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorized in a maximum of three groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron \textbf{has the most differences with} the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are \textbf{more similar to each other than to the ones in the left neurons}; both groups are starbursting and have strong emission lines.
            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the \textbf{\textcolor{red}{spectra}} to become flatter at shorter wavelengths. 
            The flatter UV \textbf{\textcolor{red}{spectra}} make these two templates more similar to quiescent galaxies than to other starbursts.
            Therefore, in the networks, SB5 and SB6 types \textbf{\textcolor{red}{are grouped close to the quiescent galaxy templates}}.

@@

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct \textbf{\textcolor{red}{spectral types}}, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
            \end{subfigure}
            \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*}

            In Fig.~\ref{fig: 1by22T}, we can see twelve distinct groups.
            Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
            \textbf{Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks.
            This figure is a good example of the problem of using one-dimensional SOMs to explore the data.
            Since are the templates are forced to be arranged in a linear array, the SB6 and Sc groups are isolated and not connected to any other groups.
            However, in a two-dimensional map, due to the connection of each neuron to 6 more neurons, template galaxies have more degrees of freedom to find their relation with other neurons.
            As a big picture, Fig.~\ref{fig: 1by22T}} shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
            The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
            This template has the most extinction and \textbf{\textcolor{red}{ the general shape of its spectrum}} has more similarity to \textbf{\textcolor{red}{quiescent galaxies}} than to other starburst types.

@@

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the spectra derived from the fitted SEDs of the 142-galaxy sample from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have \textbf{\textcolor{red}{spectral types}} similar to those of the quiescent galaxies and the \textbf{\textcolor{red}{spectral types}} of the rest are similar to the starburst galaxies.
            The lower left panel shows the \textbf{\textcolor{red}{median spectrum}} of the 80 galaxies that were classified as quiescent. 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the \textbf{\textcolor{red}{spectra}} clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar \textbf{\textcolor{red}{spectral types}} to Sa galaxies, but with stronger emission lines.
            The \textbf{\textcolor{red}{median spectrum}} in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2_fluxdensity.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy \textbf{\textcolor{red}{spectra}} from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 \textbf{\textcolor{red}{spectra are classified into the quiescent group}} while the 62 of the 142 spectra are categorized as starburst galaxies. Lower panel: \textbf{\textcolor{red}{median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}}}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's \textbf{\textcolor{red}{spectrum}} predominantly decides to which group the galaxy belongs.
            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.

            Fig.~\ref{fig: 1by3V} presents the result of classifying the \textbf{\textcolor{red}{spectra}} of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to \textbf{\textcolor{red}{the quiescent group, and 47 belong to the starburst group}}. 
            However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).

@@

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
           As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            The lower panels present the \textbf{\textcolor{red}{median spectra}} of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 \textbf{\textcolor{red}{median spectra}} in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.

@@

            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that the \textbf{\textcolor{red}{spectra}} of galaxies in the cluster are very similar to those of the template.
            Otherwise, we can conclude that the \textbf{\textcolor{red}{spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates}}.
            For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with \textbf{\textcolor{red}{spectral type}} similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            \textbf{\textcolor{red}{19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.}}
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neuron have similar \textbf{\textcolor{red}{spectra}} to Sb type galaxies, and the \textbf{\textcolor{red}{spectra}} of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with \textbf{\textcolor{red}{spectra}} comparable to types SB1 and SB2.

@@

           \textbf{With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies into intermediate groups.
            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.}

@@

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from \textbf{\textcolor{red}{quiescent galaxies to starburst.}}
       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the \textbf{\textcolor{red}{spectra}}, as expected since the spectral types are also based on {\em CIGALE} fitting.

@@

        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
        The colours show the galaxy types, where B type galaxies are shown with light grey (red in the online version) and SB1 types are shown with black (blue in the online version).
        The lighter grey (redder in the online version) the colour, the more similarity with quiescent galaxies, while the medium grey to black (purple to blue in the online version) colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with \textbf{\textcolor{red}{spectra}} similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with \textbf{more precision} than those two, in all three plots.
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their \textbf{\textcolor{red}{spectral type}}.

        \citetalias{Noll09} studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
        They found that for \textbf{\textcolor{red}{quiescent galaxies}} (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
        Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
        Whether this dependence is real or not, our results here show that using self-organizing maps can separate \textbf{\textcolor{red}{spectra}} of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.

       \textbf{One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
       Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. 
       The median properties of the spectral groups change on going from one end of the SOM to the other.
       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
       Therefore, by using the SOM method, we not only study galaxies in different clusters, we also can study the trends between them as well.}

>>>>

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
    Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
    We also applied the K-means clustering method (Section~\ref{sec: Kmeansvssom}) to both the template and sample galaxies and compared the results with the results of the 1D SOMs.
    For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network to be $12\times12$ and created two types of SOM to show different applications of 2D SOMs.

@@

            Figs.~\ref{fig: 1by2T} --~\ref{fig: 1by22T} show the results of the training networks.  %(the remaining networks are shown in Appendix~\ref{app: high_Z_1d_soms}).
            The upper part of the figures shows the neurons and the relative distances between their weights. 
            As mentioned in Section~\ref{sec: method_somz}, an increase in the darkness of colours between neurons represents an increase in relative distance between the neurons.
            The lower panels of the figures show the number of \citetalias{Kinney96} templates that are placed in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                  \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption[Results of training network in $1\times2$~grid]{Results of training network in $1\times2$~grid. The upper panel is a distance map and the lower panel is a hit map. In this network, 5 of the templates from \citet{Kinney96} are categorized as quiescent galaxies and the rest are starbursts. Because of their strong emission lines, Sc galaxies are moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

@@

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorized in a maximum of three groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron has the most differences with the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} to Fig.~\ref{fig: 1by3T} shows that the starburst templates are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are more similar to each other than to the ones in the left neurons; both groups are starbursting and have strong emission lines.
            On the other hand, the SB5 and SB6 templates have the highest internal extinctions; this causes the spectra to become flatter at shorter wavelengths. 
            The flatter UV spectra make these two templates more similar to quiescent galaxies than to other starbursts.
            Therefore, in the networks, SB5 and SB6 types are grouped close to the quiescent galaxy templates.

@@

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct spectral types, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
            \begin{figure*}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
                \end{subfigure}
                \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
                \label{fig: 1by22T}
            \end{figure*}

            In Fig.~\ref{fig: 1by22T}, we can see twelve distinct groups.
            Five groups in the left-side neurons are separated from the rest of the groups with two dark-grey colours between them.
            Five groups in the right-side neurons are separated from the rest by the black colour, and Sc and SB6 galaxies are in two separate blocks.
            This figure is a good example of the problem of using one-dimensional SOMs to explore the data.
            Since are the templates are forced to be arranged in a linear array, the SB6 and Sc groups are isolated and not connected to any other groups.
            However, in a two-dimensional map, due to the connection of each neuron to 6 more neurons, template galaxies have more degrees of freedom to find their relation with other neurons.
            As a big picture, Fig.~\ref{fig: 1by22T} shows that even though the galaxies are clustered in twelve groups, there still remain only two main distinct groups.
            The closest occupied neuron in the starburst side of the SOM, belongs to the SB6 type. 
            This template has the most extinction and  the general shape of its spectrum has more similarity to quiescent galaxies than to other starburst types.

@@

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the spectra derived from the fitted SEDs of the 142-galaxy sample from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have spectral types similar to those of the quiescent galaxies and the spectral types of the rest are similar to the starburst galaxies.
            The lower left panel shows the median spectrum of the 80 galaxies that were classified as quiescent. 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the spectra clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar spectral types to Sa galaxies, but with stronger emission lines.
            The median spectrum in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2_fluxdensity.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy spectra from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies. Lower panel: median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decides to which group the galaxy belongs.
            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.

            Fig.~\ref{fig: 1by3V} presents the result of classifying the spectra of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}): 66 of the galaxies belong to the quiescent group, and 47 belong to the starburst group. 
            However, 29 of the galaxies are similar to starbursts in some, but not all, of their features. 
            Galaxies in this group have strong emission lines and are ultraviolet-bright, but they also have a strong 4000\AA~break, which makes them cluster closer to the quiescent galaxies (middle panel in the lower part of Fig.~\ref{fig: 1by2V}).

@@

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
            As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            The lower panels present the median spectra of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 median spectra in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.

@@

            Comparing the upper panel of Fig.~\ref{fig: 1by22V} with the lower panel of Fig.~\ref{fig: 1by22T} shows that the occupied neurons are not necessarily the same.
            If a cluster from the \citetalias{Hossein12} sample fills the same neuron as a \citetalias{Kinney96} template, we can conclude that the spectra of galaxies in the cluster are very similar to those of the template.
            Otherwise, we can conclude that the spectra of galaxies in the cluster are (dis)similar to two of the \citetalias{Kinney96} templates.
            For the latter case, the colours establish which template has greater similarity to the \citetalias{Hossein12} cluster.

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with spectral type similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neuron have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with spectra comparable to types SB1 and SB2.

@@

           With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies into intermediate groups.
            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.

@@

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst.
       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs, as expected since the spectral types are also based on {\em CIGALE} fitting.

@@

        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
        The colours show the galaxy types, where B type galaxies are shown with light grey (red in the online version) and SB1 types are shown with black (blue in the online version).
        The lighter grey (redder in the online version) the colour, the more similarity with quiescent galaxies, while the medium grey to black (purple to blue in the online version) colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with more precision than those two, in all three plots.
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their spectral type.

        \citetalias{Noll09} studied a correlation between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
        They found that for quiescent galaxies (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
        Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
        Whether this dependence is real or not, our results here show that using self-organizing maps can separate spectra of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.

       One of the key features of SOMs is the ability to not only classify objects but to provide an {\em ordered} classification. 
       Figure~\ref{fig: props_vs_props} shows that the SOM correctly determines an ordering of the physical properties of the galaxy models used to make the classified spectra. 
       The median properties of the spectral groups change on going from one end of the SOM to the other.
       K-means clustering and supervised ANNs can sort galaxy spectra into classes but do not naturally order them.
       Therefore, by using the SOM method, we not only study galaxies in different clusters, we also can study the trends between them as well.

    \subsection{Comparison of the self-organizing maps and K-means methods}
    \label{sec: Kmeansvssom}
